Javelins with hyper3 objects

### 2025-12-28 inst/javelin.Rmd
typos

Above we see that Chopra threw the longest and second-longest throws
of 87.58m and 87.03 respectively; Vadlejch threw the third-longest
throw of 86.67m, and so on.  `NA` entries correspond to no-throws.  It
is easy to plot the data in visual form:

>>>>

Above we see that Chopra threw the longest and second-longest throws
of 87.58 and 87.03 respectively (all measurements are in meters);
Vadlejch threw the third-longest throw of 86.67, and so on.  `NA`
entries correspond to no-throws.  It is easy to plot the data in
visual form:
